Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2017-03-24 paper/presentation/DASFAA_presentation.tex
use tikz and textblock for beamer

\documentclass{beamer}

@@

\setbeamercolor{title}{bg=red!65!black,fg=white}
\usepackage{bm}
\usepackage{graphics} % used for scalebox
\usepackage{multirow}%used for multicolumn
\usepackage{array}%used for vrule
\usepackage{subfigure}
\usepackage{threeparttable} % used for footnotes in table

@@

\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\author{Weijing Huang, Tengjiao Wang, Wei Chen, Yazhou Wang}
\institute[EECS, Peking University]{School of Electronics Engineering and Computer Science, Peking University}
\date{\(\bm{@}\)DASFAA 2017, Suzhou, China}
\maketitle

@@

%------------------------------
%page 4
\begin{frame}
\frametitle{Challenges (2/2)}	
Statistics of some labeled events on Edinburgh twitter corpus.
\intextsep=5pt plus 3pt minus 1pt % 调整表格与正文的上间距
\begin{table}[]
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{My caption}
\label{my-label}
\scalebox{0.65}{
\begin{tabular}{|l|l|r|}
\hline
Event                                        & Date       & Event Size \\ \hline
S\&P downgrade US credit rating                  & 05/08/2011 & 656      \\ \hline
Atlantis shuttle lands                           & 21/07/2011 & 595      \\ \hline
US increases debt ceiling                        & 25/07/2011 & 485      \\ \hline
Plane with Russian hocky team Lokomotiv crashes  & 07/09/2011 & 286      \\ \hline
Amy Winehouse dies                               & 23/07/2011 & 283      \\ \hline
Gunman opens fire in youth camp in Norway        & 23/07/2011 & 260      \\ \hline
Earthquake in Virginia                           & 24/08/2011 & 246      \\ \hline
First victim of London riots dies                & 09/08/2011 & 174      \\ \hline
Explosion in French nuclear plant in Marcoule    & 12/09/2011 & 135      \\ \hline
Google announces plans to bury Motorola Mobility & 15/08/2011 & 127      \\ \hline
NASA announces there might be water on Mars      & 04/08/2011 & 124      \\ \hline
Car bomb explodes in Oslo, Norway                & 22/07/2011 & 114      \\ \hline
... & ... & ... \\ \hline
Indian and Bangladesh sign a border pact         & 06/09/2011 & 25       \\ \hline
Flight 4896 crash                                & 13/07/2011 & 21       \\ \hline
First aritficial organ transplant                & 12/07/2011 & 18       \\ \hline
three men die in riots in england                & 10/08/2011 & 16       \\ \hline
rebels capture interational tripoli airport      & 21/08/2011 & 13       \\ \hline
\end{tabular}
}
\end{table}
\end{frame}

%------------------------------
%page 5
\begin{frame}
\frametitle{How about existing methods on dealing with challenges?}

@@

>>>>

% arara: pdflatex
% !arara: indent: {overwrite: on}
\documentclass{beamer}

@@

%-chage foot part-------------------------------
\makeatother
\setbeamertemplate{footline}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.17\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshortauthor
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.46\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
    \usebeamerfont{title in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.37\paperwidth,ht=2.25ex,dp=1ex,center]{date in head/foot}% 
  \insertdate \hspace{0.2cm}
    \insertframenumber{} / \inserttotalframenumber\hspace*{1ex}
  \end{beamercolorbox}}%
  \vskip0pt%
}
\makeatletter
\setbeamertemplate{navigation symbols}{}
%--------------------------------

%-chage titlepage's font-------------------------------
\setbeamercolor{title}{bg=red!65!black,fg=white}
\usepackage{bm}
\usepackage{comment}
\usepackage{graphics} % used for scalebox
\usepackage{multirow}%used for multicolumn
\usepackage{array}%used for vrule
\usepackage{subfigure}
\usepackage{threeparttable} % used for footnotes in table

%---set tikz highlighter------------------------
\usepackage{multirow, booktabs, dcolumn, color} % Tables
\usepackage[beamer,customcolors]{hf-tikz}
\usetikzlibrary{calc}
% To set the hypothesis highlighting boxes red.
\tikzset{hl/.style={
    set fill color=red!80!black!40,
    set border color=red!80!black,
  },
}
%-----------------------------------------------

%---set tikz marker-----------------------------
\usepackage{tikz}
\usetikzlibrary{positioning}
\tikzset{>=stealth}

\newcommand{\tikzmark}[3][]{\tikz[overlay,remember picture,baseline] \node [anchor=base,#1](#2) {#3};}
%-----------------------------------------------

%---set textblock----------------------------
\usepackage[absolute,overlay]{textpos}
%--------------------------------------------------------

@@

\title[Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection]{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\author[Weijing Huang, et,al.]{Weijing Huang, Tengjiao Wang, Wei Chen, Yazhou Wang}
\institute[EECS, Peking University]{School of Electronics Engineering and Computer Science, Peking University}
\date{\(\bm{@}\)DASFAA 2017, Suzhou, China}
\maketitle

@@

%------------------------------
%page 4
\begin{frame}
\frametitle{Challenges (2/2)}	
\tikzmark{comment18}\,

\intextsep=5pt plus 3pt minus 1pt % 调整表格与正文的上间距
\begin{table}[]
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{Statistics of labeled events on Edinburgh twitter corpus.}
\label{my-label}
\scalebox{0.65}{
\begin{tabular}{|l|l|r|}
\hline
Event                                        & Date       & Event Size \\ \hline
S\&P downgrade US credit rating                  & 05/08/2011 & 656      \\ \hline
Atlantis shuttle lands                           & 21/07/2011 & 595      \\ \hline
US increases debt ceiling                        & 25/07/2011 & 485      \\ \hline
Plane with Russian hocky team Lokomotiv crashes  & 07/09/2011 & 286      \\ \hline
Amy Winehouse dies                               & 23/07/2011 & 283      \\ \hline
Gunman opens fire in youth camp in Norway        & 23/07/2011 & 260      \\ \hline
Earthquake in Virginia                           & 24/08/2011 & 246      \\ \hline
First victim of London riots dies                & 09/08/2011 & 174      \\ \hline
Explosion in French nuclear plant in Marcoule    & 12/09/2011 & 135      \\ \hline
Google announces plans to bury Motorola Mobility & 15/08/2011 & 127      \\ \hline
NASA announces there might be water on Mars      & 04/08/2011 & 124      \\ \hline
Car bomb explodes in Oslo, Norway                & 22/07/2011 & 114      \\ \hline
... & ... & ... \\ \hline
\tikzmarkin<1>[hl]{bH1}Indian and Bangladesh sign a border pact         & 06/09/2011 & 25       \\ \hline
Flight 4896 crash                                & 13/07/2011 & 21       \\ \hline
First aritficial organ transplant                & 12/07/2011 & 18       \\ \hline
three men die in riots in england                & 10/08/2011 & 16       \\ \hline
rebels capture interational tripoli airport      & 21/08/2011 & 13       \tikzmarkend{bH1} \\ \hline
\end{tabular}
}
\end{table}

 \begin{textblock}{0.1}(14,12)
  \footnotesize{Small events with fewer tweets}
 \end{textblock}

%\begin{comment}
%------------------------------
%page 5
\begin{frame}
\frametitle{How about existing methods on dealing with challenges?}

@@

%\end{comment}
